EpisoPass: Password Management based on Episodic Memories

### 2016-08-30 paper/Password2016/paper.tex
Frankのコメントに対応中

The idea of using episodic memories for authentication has a long
history and early papers suggested using episodic memories for
creating passwords. Authentication using secret questions is sometimes
referred to as ``cognitive
passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches
have been used as an alternative to password-based authentication
systems.
%
While cognitive passwords were aimed to be alternatives to
password-based systems, EpisoPass is a system for supporting
password-based systems using episodic memories.

@@

@@

Various types of image-based authentication systems have been proposed recently%
\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
based on the realisation that images are easier to remember than text
given they are usually more directly linked to episodic memories.
However, some image-based authentication systems request
users to remember new secrets related to the images instead of
using the users' old episodic memories.
This turns out to be not much easier to remember than passwords.
%
% \marginnote{This statement seems to contradict what you said above
%   about it being easy to find images. Probably the phrasing just needs
%   a bit of refinement.}

@@

EpisoPass has been used by the authors for more than three years
for various services including Twitter, Facebook, Amazon, Skype, {\it etc}.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, managing multiple passwords was a significant challenge
for the authors. We now have all the information for generating passwords 
stored in the cloud and no problems have arisen from this during this period.
%
Since the introduction of our browser extension, visiting the EpisoPass 
service has now become unnecessary, making authentication to the various
services even easier.

The EpisoPass service is available via the Website and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}. EpisoPass currently has only a small user-base, one major
reason being that most people cannot fully understand the
idea behind EpisoPass, and may not trust it without the 
support of a well-known IT company.
% nor supported by famous computer users.
Another reason is that it's difficult for general users to 
assess the security of EpisoPass.
Since the intention is for the questions and answers to be obvious
to those that know them (but not to others), users may lack
confidence in their answers being unknown to others.
Any authentication system expecting widespread use must take
such psychological issues seriously, and we hope to address 
such issues in future work.

@@

% \subsubsection*{Acknowledgments.} 
% The work presented in this paper was in part conducted while on
% sabbatical at the University of Cambridge, hosted by Frank Stajano and
% the Pico group, and supported by EPSRC grant number ??????.

>>>>

The idea of using episodic memories for authentication has a long
history and early papers suggested using episodic memories for
creating passwords \cite{Barton:Password}.
Authentication using secret questions is sometimes
referred to as ``cognitive
passwords''\cite{Zviran:1990:UAC:100512.100538}, and such approaches
have been used as an alternative to password-based authentication
systems.
%
While cognitive passwords were aimed to be alternatives to
password-based systems, EpisoPass is a system for supporting
password-based systems using episodic memories.

@@

\subsection{Password entry time}

Answering to many questions takes much longer time than typing a
remembered password, so most people may prefer typing password
rather than using EpisoPass if they have to log in to a service frequently.
The tradeoff betwee security and usability has long been a big issue
of authentication systems \cite{Braz:2007:DTU:1778331.1778344},
but we believe we can approach the best solution by
improving the user interface of answering questions.

% Frank's comment
% 3.11. It takes a rather long time to enter one password!''
% should also be discussed, and may be a killer in some cases. Maybe
% Episopass is good for infrequently used passwords where the penalty of
% a slow login is less relevant.

@@

Various types of image-based authentication systems have been proposed recently
\cite{Biddle:2012:GPL:2333112.2333114,GraphicalPasswords},
based on the realisation that images are easier to remember than text
given they are usually more directly linked to episodic memories.
However, some image-based authentication systems request
users to remember new secrets related to the images instead of
using the users' old episodic memories.
This turns out to be not much easier to remember than passwords.
%
% \marginnote{This statement seems to contradict what you said above
%   about it being easy to find images. Probably the phrasing just needs
%   a bit of refinement.}

@@

EpisoPass has been used by the authors for more than three years
for various services including Twitter, Facebook, Amazon, Skype, {\it etc}.
% Since passwords for these services are remembered on the browser,
% EpisoPass is used only once in one week at most.
%
Before using EpisoPass, managing multiple passwords was a significant challenge
for the authors. We now have all the information for generating passwords 
stored in the cloud and no problems have arisen during this period.
%
Since the introduction of our browser extension, visiting the EpisoPass 
service has now become unnecessary, making authentication to the various
services even easier.

The EpisoPass service is available via the Website and the source code is
available on GitHub\footnote{
  (url removed for double-blind review)
  % \url{https://EpisoPass.com/},
  % \url{https://github.com/masui/EpisoPass}
}. EpisoPass currently has only a small user-base, one major
reason being that most people cannot fully understand the
idea behind EpisoPass, and may not trust it without the 
support of a well-known IT company.
% nor supported by famous computer users.
Another reason is that it's difficult for users to
assess the security of EpisoPass.
Since the intention is for the questions and answers to be obvious
to those that know them (but not to others), users may lack
confidence in their answers being unknown to others.
Any authentication system expecting widespread use must take
such psychological issues seriously, and we hope to address 
such issues in future work.

@@

% \subsubsection*{Acknowledgments.}
% This paper was written while on
% sabbatical at the University of Cambridge, hosted by Frank Stajano and
% the Pico group, and supported by EPSRC grant number
% EPSRC IRIS grant EP/M019055/1 on  ``Future Authentication Systems''.
